Empowering Domain Recursion in Symmetric Weighted First-Order Model Counting

### 2021-12-27 talk/talk.tex
First implementation of (working?) breadth-first search

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[style=verbose]{biblatex}
\usepackage{amsmath}
\usepackage{tikz}

@@

\author{Paulius Dilkas}
\title{Empowering (Domain) Recursion in Symmetric Weighted First-Order Model Counting}
\date{}

@@

>>>>

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[style=verbose]{biblatex}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{tikz}

\usetheme{CambridgeUS}

@@

\author{Paulius Dilkas}
\title[Empowering Domain Recursion]{Empowering Domain Recursion in Symmetric Weighted First-Order Model Counting}
\date{}

@@

\begin{frame}{Overview}
  \begin{block}{Hypothesis}
    Partial injections can be counted in polynomial time using (a modification of) \textsc{ForcLift}.
  \end{block}
  \begin{block}{Key Ideas \& Progress}
    \begin{itemize}
    \item[\textcolor{green}{100\%}] Support for cycles in circuits
    \item[\textcolor{green}{95\%}] Transforming $X \ne x$ constraints into domain reductions $\Delta' \coloneqq \Delta \setminus \{ x \}$
    \item[\textcolor{green}{95\%}] A less restrictive version of domain recursion
    \item[\textcolor{orange}{90\%}] A hybrid search algorithm
    \item[\textcolor{red}{0\%}] Complexity identification
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Search}
  \begin{definition}
    A \alert{partial solution} (i.e., a search node) is a tuple consisting of:
    \begin{itemize}
    \item a partial circuit, i.e., a \textsc{ForcLift}-style DAG,
      \begin{itemize}
      \item Each node type has a predefined out-degree.
      \item Some of them may be `arcs to nothing'.
      \end{itemize}
    \item a cache (i.e., a formula $\to$ node hashmap), used to identify opportunities for recursion,
    \item a list of formulas that still need to be compiled, listed in a particular order.
    \end{itemize}
  \end{definition}
  % Sink and non-sink rules
\end{frame}

\begin{frame}{Search}
  Some rules are applied in a greedy manner:
  \begin{itemize}
  \item identifying the current formula as something that's already been compiled using the cache;
  \item sink nodes: tautologies, contradictions, unit clauses;
  \item some formula-simplifying rules;
  \item unit propagation.
  \end{itemize}
  And some rules are used to branch out into several possibilities:
  \begin{itemize}
  \item independent subtheories,
  \item shattering,
  \item ground decomposition,
  \item inclusion-exclusion,
  \item independent partial grounding,
  \item counting,
  \item (my version of) domain recursion.
  \end{itemize}
\end{frame}
